\begin{center}
  \large
  \textbf{\emph{MARKETPLACE NFT} FOR \emph{METAVERSE} BASED ON \emph{SMART CONTRACT} OF \emph{ETHEREUM BLOCKCHAIN}}
\end{center}
% Menyembunyikan nomor halaman
\thispagestyle{empty}

\begin{flushleft}
  \setlength{\tabcolsep}{0pt}
  \bfseries
  \begin{tabular}{lc@{\hspace{6pt}}l}
  Student Name / NRP&: &Renaka Agusta / 07211940000011\\
  Department&: &Computer Engineering FTEIC - ITS\\
  Advisor&: &1. Mochamad Hariadi, S.T., M.Sc., Ph.D.\\
  & & 2. Dr. Surya Sumpeno, S.T, M.Sc.\\
  \end{tabular}
  \vspace{4ex}
\end{flushleft}
\textbf{Abstract}

% Isi Abstrak
Non Fungible Token (NFT) is type of token in blockchain that represents ownership of digital asset. In the beginning of NFT emergence, NFT is used to ensure the originality of digital arts. 
After that the use case of NFT is wider, the example is the use of NFT as assets in games that bring metaverse concept. 
Metaverse is concept that brings reality into digital environment. The implementation of Blockchain and NFT into metaverse is developed cause some reasons such as the existence of universal currency with cryptocurrency, system security, decentralization, and guarantee of asset originality. 
Although brings some advantages, there are some bad effects that appears of NFT implementation into metaverse.  Recently most of NFT Marketplace implement basic functions of ERC-721 Smart Contract that have limited features. This implementation makes potential of revenue of ownership is limited where the owner can only get revenue from sale their assets which is in this case is NFT. In reality owners not only get revenue from sale their asset but also  from rent their assets even share their ownership. Of course this bad effect against the metaverse concept that wants bring real world to digital world. Not only that, this condition also makes the liquidity of asset lower. The liquidity of asset is importance thing because this one can be importance factor to pricing movement of its asset.
Because of that there is a need a NFT Marketplace that can ensure the potential revenue of asset ownership and liquidity like in real world that is line with metaverse concept.

\vspace{2ex}
\noindent
\textbf{Keywords: \emph{Rocket, Anti-gravity, Meong}}